Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-06 paper.tex
Section 2.2 (not finished)

\begin{abstract}
The \textit{scikit-learn} project is an increasingly popular open source machine
learning library designed to be simple and efficient, accessible to non-experts,
and reusable in various contexts. In this paper, we present and discuss our
design choices for the application programming interface (API) of the project.
In particular, we describe the core \textit{estimator} interface shared by all
learning and processing units in the library and then discuss its advantages in
terms of composition and reusability. The paper also comments on implementation
details specific to the Python ecosystem and highlights obstacles faced by users
and developers of the library.
\end{abstract}

@@

In this section, we discuss the general principles of the application programming
interface (API) of \textit{scikit-learn}. We first specify the representation
of data and then proceed by describing the interface shared by all learning
processing units of the library. We then discuss the composition and reusability
advantages of that interface.

@@

\subsection{Estimators}

% TODO describe transformer vs. classifiers/regressors

The bulk of the scikit-learn application programming interface
consists of so-called \textit{estimator} objects.
All learning algorithms for classification, regression and clustering
are offered as such objects,
but so are feature extraction, feature selection and dimensionality reduction
algorithms.

Construction and application of an estimator object
proceeds in a way that is somewhat reminiscent of partial function application.
The constructor, \texttt{\_\_init\_\_}\footnote{
  Strictly speaking, \texttt{\_\_init\_\_} is Python's
  class \textit{initialization} method,
  while \texttt{\_\_new\_\_} is the constructor.
  The distinction is not relevant to the present description of scikit-learn.}
takes a set of named (hyper-)parameters
and attaches these to the estimator as public attributes.\footnote{
  The Python language does not actually distinguish between public and private
  attributes and methods,
  but by convention, any identifier prefixed with an underscore (\texttt{\_})
  is considered ``a non-public part of the API\ldots
  an implementation detail and subject to change without notice.''
  \Citep{pythontut}
  }
It never performs actual learning, nor does it even see a training set.

>>>>

\begin{abstract}
The \textit{scikit-learn} project is an increasingly popular open source machine
learning library designed to be simple and efficient, accessible to non-experts,
and reusable in various contexts. In this paper, we present and discuss our
design choices for the application programming interface (API) of the project.
In particular, we describe the simple and limited interface shared by all
learning and processing units in the library and then discuss its advantages in
terms of composition and reusability. The paper also comments on implementation
details specific to the Python ecosystem and highlights obstacles faced by users
and developers of the library.
\end{abstract}

@@

In this section, we discuss the general principles of the application
programming interface (API) of \textit{scikit-learn}. We first specify the
representation of data and then proceed by describing the interface shared by
all objects of the library. We then discuss the composition and reusability
advantages of that interface.

@@

\subsection{Estimators, predictors and transformers}

All objects within \textit{scikit-learn} share a uniform common basic API
consisting of three complementary interfaces: an \textit{estimator} interface
for building and fitting objects, a \textit{predictor} interface for making
predictions and a \textit{transformer} interface for converting data.
As much as possible, our design choices have been guided so as to avoid
the proliferation of framework code. We try to adopt simple conventions and
to limit to a minimum the number of methods an object must implement.

\textbf{Estimators.} The \textit{estimator} interface is at the core of the
library. It defines instantiation mechanisms of objects and exposes a
\texttt{fit} method for learning a model from training data.  All supervised and
unsupervised learning algorithms (e.g., for classification, regression or
clustering) are offered as objects implementing that interface. Machine
learning tasks like feature extraction, feature selection or dimensionality
reduction are also provided as estimators.

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes\footnote{Python does not actually
distinguish between public and private  attributes or methods. By convention
however, any identifier prefixed with an underscore is considered a non-public
part of the API~\citep{pythontut}.} and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, appropriate default hyper-parameter values are provided for all
built-in estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible out-of-box for
non-experts. Finally, the constructor of an estimator never performs any actual
learning, nor does it even see any training dataset. Its only goal
is to set the parameter values and freeze the behavior of the estimator.

\vspace{3cm}

% The bulk of the scikit-learn application programming interface
% consists of so-called \textit{estimator} objects.
% All learning algorithms for classification, regression and clustering
% are offered as such objects,
% but so are feature extraction, feature selection and dimensionality reduction
% algorithms.

% Construction and application of an estimator object
% proceeds in a way that is somewhat reminiscent of partial function application.
% The constructor, \texttt{\_\_init\_\_}\footnote{
%   Strictly speaking, \texttt{\_\_init\_\_} is Python's
%   class \textit{initialization} method,
%   while \texttt{\_\_new\_\_} is the constructor.
%   The distinction is not relevant to the present description of scikit-learn.}
% takes a set of named (hyper-)parameters
% and attaches these to the estimator as public attributes.\footnote{
%   The Python language does not actually distinguish between public and private
%   attributes and methods,
%   but by convention, any identifier prefixed with an underscore (\texttt{\_})
%   is considered ``a non-public part of the API\ldots
%   an implementation detail and subject to change without notice.''
%   \Citep{pythontut}
%   }
% It never performs actual learning, nor does it even see a training set.
